Meta-analysis of the Interoceptive Accuracy Scale

### 2025-10-20 analysis/study2.qmd
Update study2.qmd

# names(df1a)
# names(df1b)
# names(df2)  #TAS(20 items), MAIA(37 items), ICQ (20 items), BPQ(46 items), BVAQ (40 items)
# names(df3)  # TAS (20), BPQ (46)
# names(df4)  # BPQ(26), PBCS (private bodily consciousness?), MAIA (37), BAQ (18), BRS (4)
# names(df5)  
# names(df6)  # PHQ2 (2 items), GAD2 (2 items), SSS8, IATS
# names(df7a)  # STAIT (20), MAIA(37), CES (not reported in the paper), FFMQ (39), NEOFFI (12)
# names(df7b)  # BPQ (12), PHQ15 (15), PHQ9 (9), MAIA (37), STAIT(20), 
# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ  - no individual items
# names(df8a)  # EDI (10), BPQ (12)
# names(df8b)  # PHQ9 (9), PHQ15 (15), TAS (20)
# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI (15), DBIA, BO, EQ
# names(df10)  # ASQ(28), BPD(9), GCBS (15), IPIP6 (24), LIE (16), MAIA(37), PHQ4 (4), PI (32), PID (25), SPQ (32)
# names(df11)  # PHQ4 (4), STAIT5 (5), BDI (21), MAIA (37)
# names(df12) # MAIA (37), PI (99), 
# names(df13) # PI (18), MAIA (37)
# names(df14) # MAIA(37), TAS  (20), MFQ(DEP, 13), STAI(ANX, 20)
# names(df15) 
# names(df16) # MAIA (37), GAD (7), PHQ9 (9)
```

@@

pool_coef <- function(with = "Age", component = "Demographic", name = with, unequalrange=FALSE) {
  rez <- data.frame()
  for(intero in vars_intero) {
    data <- data.frame() 
    for(dataset in list(df1a, df1b, df2, df3, df4, 
                     df5, df6, df7a, df7b, df7c, 
                     df8a, df8b, df9, df10, df11, 
                     df12, df14, df15, df16)) {
      if (with %in% names(dataset)) {
        d <- dataset[c(with, intero, "Sample")]
        data <- rbind(data, d)
      }
    }

@@

    if (with == "Gender") {
      data <- data[data$Gender != "Other",]
      data$Gender <- factor(data$Gender, levels = c("Male", "Female"))
      f <- as.formula(paste0(intero, "~", with, " + (", with, "|Sample)"))
      f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
    } else {
      f <- as.formula(paste0(intero, "~", with, " + (", with, "|Sample)"))
      f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
    }

    # if(length(unique(data$Sample)) == 1)
    m <- glmmTMB::glmmTMB(f, data = data)
    type <- "Full"
    if(!insight::is_converged(m)) {
      m <- glmmTMB::glmmTMB(f2, data = data)
      type <- "Reduced"
    }
    out <- parameters::parameters(m)[2, ] |> 
      select(r = Coefficient, CI_low, CI_high, p) |> 
      as.data.frame()
    out$var_Interoception <- intero
    out$var_Correlate <- with
    out$Component <- component
    out$Type <- type
    out$Converged <- insight::is_converged(m)
    out$N <- nrow(data)
    rez <- rbind(rez, out)

@@

data <- pool_coef(with = "Gender", component = "Demographic", name = "Gender (Female - Male)")
```

@@

data <- rbind(data, pool_coef(with = "Age", component = "Demographic", unequalrange=TRUE))
```

@@

data <- rbind(
  data,
  pool_coef(with = "MAIA_AttentionReg", component = "MAIA", name = "Attention Regulation", unequalrange=TRUE),
  pool_coef(with = "MAIA_BodyListening", component = "MAIA", name = "Listening", unequalrange=TRUE),
  pool_coef(with = "MAIA_Trusting", component = "MAIA", name = "Trusting", unequalrange=TRUE),
  pool_coef(with = "MAIA_EmoAwareness", component = "MAIA", name = "Emotional Awareness", unequalrange=TRUE),
  pool_coef(with = "MAIA_NotDistracting", component = "MAIA", name = "Not Distracting", unequalrange=TRUE),
  pool_coef(with = "MAIA_Noticing", component = "MAIA", name = "Noticing", unequalrange=TRUE),
  pool_coef(with = "MAIA_NotWorrying", component = "MAIA", name = "Not Worrying", unequalrange=TRUE),
  pool_coef(with = "MAIA_SelfReg", component = "MAIA", name = "Self Regulation", unequalrange=TRUE)
)
```

@@

data <- rbind(data, pool_coef(with = "ICQ", component="Alexithymia", name = "ICQ", unequalrange=TRUE))
```

data <- rbind(
  data,
  pool_coef(with = "BPQ_BodyAwareness", component="BPQ", name = "Body Awareness (BPQ)",unequalrange=TRUE),
  pool_coef(with = "BPQ_AutonomicReactivity", component="BPQ", name = "Autonomic Reactivity (BPQ)",unequalrange=TRUE)
  )
```

@@

data <- rbind(
  data,
  pool_coef(with = "TAS_DIF", component="Alexithymia", name = "Difficulties Identifying Feelings (TAS)", unequalrange=TRUE),
  pool_coef(with = "TAS_DDF", component="Alexithymia", name = "Difficulties Describing Feelings (TAS)", unequalrange=TRUE),
  pool_coef(with = "TAS_EOT", component="Alexithymia", name = "External Thinking (TAS)",unequalrange=TRUE),
  pool_coef(with = "BVAQ_Affective", component="Alexithymia", name = "Affective (BVAQ)"), 
  pool_coef(with = "BVAQ_Cognitive", component="Alexithymia", name = "Cognitive (BVAQ)")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "PHQ15_Sum", component="Mood", name = "Somatic Concerns (PHQ-15)",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Mood", name = "Depression (PHQ-9)",unequalrange=TRUE), 
  pool_coef(with = "BDI_Sum", component="Mood", name = "Depression (BDI)"), 
  pool_coef(with = "PHQ4_Depression", component="Mood", name = "Depression (PHQ-4)"),
  pool_coef(with = "DEP", component = "Mood", name = "Depression (MFQ)")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "STAIT_Mean", component="Mood", name = "Anxiety (STAI-T)",unequalrange=TRUE), 
  pool_coef(with = "PHQ4_Anxiety", component="Mood", name = "Anxiety (PHQ-4)"),
  pool_coef(with = "GAD7_Sum", component="Mood", name = "Anxiety (GAD-7)")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "BPD", component="Mood", name = "Boderline Personality")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "Neuroticism", component = "Personality", name = "Neuroticism",unequalrange=TRUE),
  pool_coef(with = "Agreeableness", component="Personality", name = "Agreeableness",unequalrange=TRUE),
  pool_coef(with = "Conscientiousness", component="Personality", name = "Conscientiousness",unequalrange=TRUE), 
  pool_coef(with = "Openness", component="Personality", name = "Openness",unequalrange=TRUE),
  pool_coef(with = "Extraversion", component="Personality", name = "Extraversion", unequalrange=TRUE),
  pool_coef(with = "HonestyHumility", component="Personality", name = "Honesty-Humility",unequalrange=TRUE)
)
```

## Others

@@

p <- data |>
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "BruiseBlood", "Bruise/Blood sugar"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "BreathingHeart", "Breathing/Heart"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate")) |>
         # Component = fct_relevel(
         #   Component, "Demographic", "MAIA", "Body", "Mood", "Maladaptive",
         #   "Schizotypic", "Autistic", "Personality", "Conspiracy Beliefs", "World Beliefs", "Lying Profile")) |>
  ggplot(aes(y = var_Correlate)) +
  annotate(geom = "rect", xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax=Inf, fill = "#FFF8E1") +
  annotate(geom = "rect", xmin = c(-0.3, 0.1), xmax = c(-0.1, 0.3), ymin = -Inf, ymax=Inf, fill = "#F1F8E9") +
  annotate(geom = "rect", xmin = c(-0.6, 0.3), xmax = c(-0.3, 0.6), ymin = -Inf, ymax=Inf, fill = "#E8F5E9") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  # geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
  geom_linerange(aes(color=dir, alpha=sig, xmax=r, xmin=0), linewidth = 1) +
  geom_linerange(aes(color = dir, alpha = sig, xmin = CI_low, xmax = CI_high, linewidth = log(N))) +
  # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
  # geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7),
  #                linewidth = 1) +
  facet_grid(Component ~ var_Interoception, scales = "free", space ="free", switch = "y") +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.9), guide = "none") +
  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  scale_linewidth_continuous(range = c(3, 7), guide = "none") +
  coord_cartesian(xlim = c(-0.45, 0.45)) +
  theme_modern(axis.title.space = 5) +
  labs(x = "Strength of Association (std. Beta)") +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure3.png", p, width=21*0.5, height=29.7*0.5, dpi=300, bg="white")
```

@@

Need for context-specific items (cross-modal when possible, i.E., cardioception, respiroception, etc.).

New Scale: Multimodal Interoceptive Sensitivity Scale (MISS)

>>>>

# names(df1a)
# names(df1b)
# names(df2)  #TAS(20 items), MAIA(37 items), ICQ (20 items), BPQ(46 items), BVAQ (40 items)
# names(df3)  # TAS (20), BPQ (46)
# names(df4)  # BPQ(26), PBCS (private bodily consciousness?), MAIA (37), BAQ (18), BRS (4)
# names(df5)  
# names(df6)  # PHQ2 (2 items), GAD2 (2 items), SSS8, IATS
# names(df7a)  # STAIT (20), MAIA(37), CES (not reported in the paper), FFMQ (39), NEOFFI (12)
# names(df7b)  # BPQ (12), PHQ15 (15), PHQ9 (9), MAIA (37), STAIT(20), 
# names(df7c)  # CI01 (not reported in the paper), TAS, BPQ, MAIA, ASI, ICQ  - no individual items
# names(df8a)  # EDI (10), BPQ (12)
# names(df8b)  # PHQ9 (9), PHQ15 (15), TAS (20)
# names(df9)  # ECR (Experience in Close Relationship Scale), TEAQ (touch experiences and attitudes questionnaire), STQ, TACSEN, UCLA, BFI (15), DBIA, BO, EQ
# names(df10)  # ASQ(28), BPD(9), GCBS (15), IPIP6 (24), LIE (16), MAIA(37), PHQ4 (4), PI (32), PID (25), SPQ (32)
# names(df11)  # PHQ4 (4), STAIT5 (5), BDI (21), MAIA (37)
# names(df12) # MAIA (37), PI (99), 
# names(df13) # PI (18), MAIA (37)
# names(df14) # MAIA(37), TAS  (20), MFQ(DEP, 13), STAI(ANX, 20)
# names(df15) 
# names(df16) # MAIA (37), GAD (7), PHQ9 (9)

alldata <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, 
                df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, 
                df8a=df8a, df8b=df8b, df9=df9, df10=df10, df11=df11, 
                df12=df12, df14=df14, df15=df15, df16=df16)
```

@@

pool_coef <- function(with = "Age", component = "Demographic", category = "Demographic", name = with, unequalrange=FALSE) {
  rez <- data.frame()
  for(intero in vars_intero) {
    data <- data.frame() 
    for(dataset in alldata) {
      if (with %in% names(dataset)) {
        d <- dataset[c(with, intero, "Sample")]
        data <- rbind(data, d)
      }
    }

@@

    if (with == "Gender") {
      data <- data[data$Gender != "Other",]
      data$Gender <- factor(data$Gender, levels = c("Male", "Female"))
      f <- as.formula(paste0(intero, "~", with, " + (", with, "|Sample)"))
      f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
      f3 <- as.formula(paste0(intero, "~ Sample * ", with))
    } else {
      f <- as.formula(paste0(intero, "~", with, " + (", with, "|Sample)"))
      f2 <- as.formula(paste0(intero, "~", with, " + (1|Sample)"))
      f3 <- as.formula(paste0(intero, "~ Sample / ", with))
    }

    # Mixed models
    control1 <- glmmTMB::glmmTMBControl(parallel = list(n=4, autopar = TRUE))
    control2 <- glmmTMB::glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS"), parallel = list(n=4, autopar = TRUE))
    m <- glmmTMB::glmmTMB(f, data = data, control=control1)
    type <- "Full"
    if(!insight::is_converged(m)) {
      m <- glmmTMB::glmmTMB(f, data = data, control=control2)
      type <- "Full"
    }
    if(!insight::is_converged(m)) {
      m <- glmmTMB::glmmTMB(f2, data = data, control=control1)
      type <- "Reduced"
    }
    if(!insight::is_converged(m)) {
      m <- glmmTMB::glmmTMB(f2, data = data, control=control2)
      type <- "Reduced"
    }

    # # Marginal
    # m <- lm(f3, data = data)
    # modelbased::estimate_slopes(m, trend = with)

    out <- parameters::parameters(m)[2, ] |> 
      select(r = Coefficient, CI_low, CI_high, p) |> 
      as.data.frame()
    out$var_Interoception <- intero
    out$var_Correlate <- with
    out$Category <- category
    out$Component <- component
    out$Type <- type
    out$Converged <- insight::is_converged(m)
    out$N <- nrow(data)
    rez <- rbind(rez, out)

@@

check_ranges <- function(var = "Neuroticism") {
  for(d in names(alldata)) {
    dataset <- alldata[[d]]
    if(!var %in% names(dataset)) next
    print(paste0(d, ": ", paste(round(range(dataset[[var]], na.rm=TRUE), 2), collapse = "-")))
  }
}

data <- pool_coef(with = "Gender", component = "Demographic", category = "General", name = "Gender (Female - Male)")
```

@@

# check_ranges("Age")
data <- rbind(data, pool_coef(with = "Age", component = "Demographic", category = "General", unequalrange=TRUE))
```

# check_ranges("Neuroticism")
# check_ranges("Agreeableness")
# check_ranges("Conscientiousness")
# check_ranges("HonestyHumility")

data <- rbind(
  data,
  pool_coef(with = "Neuroticism", component = "Personality", category = "General", name = "Neuroticism", unequalrange=TRUE),
  pool_coef(with = "Agreeableness", component="Personality", category = "General", name = "Agreeableness",unequalrange=TRUE),
  pool_coef(with = "Conscientiousness", component="Personality", category = "General", name = "Conscientiousness",unequalrange=TRUE), 
  pool_coef(with = "Openness", component="Personality", category = "General", name = "Openness",unequalrange=TRUE),
  pool_coef(with = "Extraversion", component="Personality", category = "General", name = "Extraversion", unequalrange=TRUE),
  pool_coef(with = "HonestyHumility", component="Personality", category = "General", name = "Honesty-Humility",unequalrange=TRUE)
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "MAIA_AttentionReg", component = "MAIA", category = "Interoception", name = "Attention Regulation - MAIA", unequalrange=TRUE),
  pool_coef(with = "MAIA_BodyListening", component = "MAIA", category = "Interoception", name = "Listening - MAIA", unequalrange=TRUE),
  pool_coef(with = "MAIA_Trusting", component = "MAIA", category = "Interoception", name = "Trusting - MAIA", unequalrange=TRUE),
  pool_coef(with = "MAIA_EmoAwareness", component = "MAIA", category = "Interoception", name = "Emotional Awareness - MAIA", unequalrange=TRUE),
  pool_coef(with = "MAIA_NotDistracting", component = "MAIA", category = "Interoception", name = "Not Distracting - MAIA", unequalrange=TRUE),
  pool_coef(with = "MAIA_Noticing", component = "MAIA", category = "Interoception", name = "Noticing - MAIA", unequalrange=TRUE),
  pool_coef(with = "MAIA_NotWorrying", component = "MAIA", category = "Interoception", name = "Not Worrying - MAIA", unequalrange=TRUE),
  pool_coef(with = "MAIA_SelfReg", component = "MAIA", category = "Interoception", name = "Self Regulation - MAIA", unequalrange=TRUE)
)
```

data <- rbind(
  data,
  pool_coef(with = "BPQ_BodyAwareness", component="Interoception", category = "Interoception", name = "Body Awareness - BPQ",unequalrange=TRUE),
  pool_coef(with = "BPQ_AutonomicReactivity", component="Interoception", category = "Interoception", name = "Autonomic Reactivity - BPQ",unequalrange=TRUE)
  )
```

@@

data <- rbind(data, pool_coef(with = "ICQ", component="Interoception", category = "Interoception", name = "Interoceptive Confusion - ICQ", unequalrange=TRUE))
```

@@

data <- rbind(
  data,
  pool_coef(with = "TAS_DIF", component="Interoception", category = "Interoception", name = "Difficulties Identifying Feelings - TAS", unequalrange=TRUE),
  pool_coef(with = "TAS_DDF", component="Interoception", category = "Interoception", name = "Difficulties Describing Feelings - TAS", unequalrange=TRUE),
  pool_coef(with = "TAS_EOT", component="Interoception", category = "Interoception", name = "External Thinking - TAS",unequalrange=TRUE),
  pool_coef(with = "BVAQ_Affective", component="Interoception", category = "Interoception", name = "Affective - BVAQ"), 
  pool_coef(with = "BVAQ_Cognitive", component="Interoception", category = "Interoception", name = "Cognitive - BVAQ")
)
```

@@

check_ranges("PHQ15_Sum")
check_ranges("PHQ9_Sum")
check_ranges("BDI_Sum")
check_ranges("PHQ4_Depression")
check_ranges("DEP")

data <- rbind(
  data,
  pool_coef(with = "PHQ15_Sum", component="Mood", category = "Mood", name = "Somatic Concerns - PHQ-15",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Mood", category = "Mood", name = "Depression - PHQ-9", unequalrange=TRUE), 
  pool_coef(with = "BDI_Sum", component="Mood", category = "Mood", name = "Depression - BDI"), 
  pool_coef(with = "PHQ4_Depression", component="Mood", category = "Mood", name = "Depression - PHQ-4"),
  pool_coef(with = "DEP", component = "Mood", category = "Mood", name = "Depression - MFQ")
)
```

@@

# check_ranges("STAIT_Mean")
# check_ranges("PHQ4_Anxiety")
# check_ranges("GAD7_Sum")

data <- rbind(
  data,
  pool_coef(with = "STAIT_Mean", component="Mood", category = "Mood", name = "Anxiety (STAI-T)", unequalrange=TRUE), 
  pool_coef(with = "PHQ4_Anxiety", component="Mood", category = "Mood", name = "Anxiety (PHQ-4)"),
  pool_coef(with = "GAD7_Sum", component="Mood", category = "Mood", name = "Anxiety (GAD-7)")
)
```

@@

check_ranges("BPD")

data <- rbind(
  data,
  pool_coef(with = "BPD", component="Mood", category = "Mood", name = "Boderline Personality")
)
```

@@

## Beliefs

@@

p <- data |>
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "BruiseBlood", "Bruise/Blood sugar"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "BreathingHeart", "Breathing/Heart"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate"),
         Category = fct_relevel(
           Category, "General", "Interoception"),
         Component = fct_relevel(Component, "Personality", "Demographic", "Interoception", "MAIA")) |> 
  group_by(Component) |> 
  mutate(var_Correlate = fct_reorder(var_Correlate, r, .fun=mean)) |>
  ungroup() |>
  ggplot(aes(y = var_Correlate)) +
  annotate(geom = "rect", xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax=Inf, fill = "#FFF8E1") +
  annotate(geom = "rect", xmin = c(-0.3, 0.1), xmax = c(-0.1, 0.3), ymin = -Inf, ymax=Inf, fill = "#F1F8E9") +
  annotate(geom = "rect", xmin = c(-0.6, 0.3), xmax = c(-0.3, 0.6), ymin = -Inf, ymax=Inf, fill = "#E8F5E9") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  # geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
  geom_linerange(aes(color=dir, alpha=sig, xmax=r, xmin=0), linewidth = 1) +
  geom_linerange(aes(color = dir, alpha = sig, xmin = CI_low, xmax = CI_high, linewidth = log(N))) +
  # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
  # geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7),
  #                linewidth = 1) +
  facet_grid(Category ~ var_Interoception, scales = "free", space ="free", switch = "y") +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.9), guide = "none") +
  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  scale_linewidth_continuous(range = c(3, 7), guide = "none") +
  coord_cartesian(xlim = c(-0.47, 0.47)) +
  theme_modern(axis.title.space = 5) +
  labs(x = "Strength of Association (std. Beta)") +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure3.png", p, width=21*1, height=29.7*1, dpi=300, bg="white")
```

@@

Need for context-specific items (cross-modal when possible, i.e., cardioception, respiroception, etc.).
